\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2021-11-22 main.Rmd
restructure the paper

Spatio-temporal data record changes of variables in spatially separated regions across time. In this article, we consider spatio-temporal vector data, which are recorded in a fixed interval and are point based, characterised by longitude and latitude, in the spatial aspect. Examples of this type of data include the house price of a city or county, climate measures from weather stations in a country, and river level data from electronic gauges.

Analysing this type of data requires less considerations on the geographical geometry type and map projection but more on how measures in these fixed locations changes across the time domain and whether these changes are related for adjacent locations. For example, when nearby areas show patterns that are regular enough, visualising spatio-temporal data can 1) discover regional time series features, i.e. trend and seasonality, 2) find the Waldo sites from the crowd, and 3) see how correlation of nearby sites changes across time.

The main difficulty in visualising this type of data is to show information in both space and time dimension with the proper level of details without information overflow. This would sometimes require aggregating the time dimension into the proper level or slicing the data into a reasonable number of subset for display. In this sense, a data structure that regulates the manipulation spatio-temporal data will benefit the analysis workflow. While many implementations focus on manipulating and visualising pure spatial or temporal data, there are not sufficient tools to deal with spatio-temporal data. The purpose of this paper is to introduce a spatio-temporal vector data structure for data analysis in R.

The rest of the paper will be divided as follows: Section 2 reviews the existing data structure for spatio, temporal, and spatio-temporal data. Section 3 presents a new data structure for spatio-temporal data: cubble. Then the paper introduces the workflow of data manipulation and visualisation with the cubble structure in Section 4. Section 5 gives some examples on how common spatial and temporal manipulations are performed with cubble and how static and interactive visualisation help to understand climate and [...] data.

@@

Below we review some structure for spatial, temporal, and spatio-temporal data.

@@

\textcolor{red}{Under the third tidy data principle [@tidydata], these are two type of observational unit and should form different tables. An example (Table 8) is also given to demonstrate the billboard dataset where there are song variables and rank variables that changes each week. The other has mentioned the lack of tool to work directly with relational data and analysis will usually need to merge the dataset into one table, which could causes errors. These days more implementations have looked at relational data structure and in R, several good examples include, `tidygraph`[@tidygraph] for graph manipulation, `dm` [@dm] for relational data model. In the domain of spatio-temporal data, @spacetime has considered four types of spatio-temporal layout. `Spatstat` [@Spatstat] an implementation of point pattern.  }

@@

<!-- Below are the how the nested and long form look like for Australia climate data, which records daily precipitation, maximum and minimum temperature for 55 stations across Australia from 2015- 2020. Notice that each station forms a group in both forms and specifically, the nested  and long form have a underlying `rowwise_df` and `grouped_df` respectively. -->

<!-- With a cubic framework on mind, different types of manipulation with cubble can be thought of as slicing the cube in various way. The table below shows how some `dplyr` verbs are mapped into the operation in a cubble. With the existing grouping on the station, additional groupping can be added with `group_by` and removed with `ungrouped`. [talk about why it is useful] -->

@@

## Manipulation

### Mutate and filter

In the first example, we want to only keep the stations that have `tmax` recorded in 2020. This requires first narrow down the records to those in 2020, determine if `tmax` is missing for each station, and then retain those stations that have `tmax` recorded. The year filtering is an operation on the time axis, so we start with the long form. Whether each station has `tmax` recorded is a result of each station, rather than of each time point, hence we need to switch to the nested form with `tamp()`. To calculate whether `tmax` is recorded, we mutate a column `tmax_missing` that takes `TRUE` if all the `tmax` in the nested list column `ts` are `NA` and `FALSE` otherwise. To get the stations that we want, we need another filter on `tmax_missing`.

```{r}
aus_climate %>% 
  stretch() %>% 
  filter(year(date) == 2020) %>% 
  tamp()
```

### Join

Now we want to select the stations that have been registered with world meteorological organisation (WMO) and the dataset `station` has a column `wmo_id` that records this information. To do this task, we first need to join the `station` dataset with our climate dataset and then filter out those stations that don't have the WMO id. Since the join is by station rather than by time, we start with the nested form and write the exact same syntax of join and filter as with tidyverse.

```{r}
# join wmo_id for each station
# to_join <- station %>% select(id, wmo_id)
# out <- climate_small %>% 
#   left_join(to_join, by = c("station" = "id")) %>% 
#   filter(!is.na(wmo_id))
# out
```

Sometimes, we would like to have station-wise and time-wise variables in the same form (i.e. when plotting glyph maps). This can also be seen as a joining task, on the long form, with the dataset to join being the metadata. `migrate()` is a verb introduced as the shortcut for `left_join()` with a cubble's metadata and below is the comparison of the two syntaxes.

```{r}
aus_climate %>% 
  stretch() %>% 
  migrate(id, lat, long)
```

  - data quality check: filter out stations have variables not properly recorded 
  - data summary: 
    - daily -> monthly/ weekly, 
    - summarise by mean for tmax/ tmin, sum for prcp
  -

## Graphics

Static + interactive -> tooltip to show additional information upon hovering

  - Where are those stations on the map? 
    - Mention mostly aero, airport, and lighthouse

# Summary

>>>>

**Spatio-temporal data + examples**  
Spatio-temporal data record changes of variables in spatially separated regions across time. In this article, we consider spatio-temporal vector data, which are recorded in a fixed interval. Examples of this type of data include the house price of a city or county, climate measures from weather stations in a country, and river level data from electronic gauges \textcolor{red}{more examples here}. \newline

<!-- and are point based, characterised by longitude and latitude, in the spatial aspect -->

**point to common feature: spatial level variables + time level variables relates to Table 13 in Tidy data paper**  
Usually, this type of spatio-temporal data don't come in as a single table. Tidy data principle (...) prescribes each type of observational unit to form a table. This would suggest two tables to store the data, one for spatial-level and  one for temporal-level. The Table 13 in the tidy data paper present a structure like this and the author argues the lack of tools to work with relational data. \newline

**My proposal**  
Recent software development in R has proposed several relational data structure: `tidygraph`[@tidygraph] for graph manipulation, `dm` [@dm] for relational data model, while spatio-temporal data could benefit from having its own relational data structure. In this paper, we propose a tidy data structure for vector spaio-temporal data.  \newline

**Section division**  
The rest of the paper will be divided as follows: Section 2 reviews the existing data structure for spatio, temporal, and spatio-temporal data. Section 3 presents a new data structure for spatio-temporal data: cubble. Then the paper introduces the workflow of data manipulation and visualisation with the cubble structure in Section 4. Section 5 gives some examples on how common spatial and temporal manipulations are performed with cubble and how static and interactive visualisation help to understand climate and [...] data. \newline

@@

**Existing packages**  
Many data structures have been proposed for spatial and temporal data, but not many for spatio-temporal data. One of the reason could be the inherent different levels of information make it inefficient to store in the same table. `spacetime`[@spacetime] proposed four space-time layouts: Full grid (STF), sparse grid(STS), irregular (STI), and trajectory (STT) based on underlying spatial structure `sp` [@sp] and temporal structure `xts`[@xts]. `spatstat` [@spatstat] implements a `ppp` class for point pattern data. More recent package `stars` [@stars] uses a spatiotemporal array to store the data and the array structure has its influence from `cubelyr` [@cubelyr], a dplyr data cube backend. \newline

**Criteria of a data structure we want**

With recent development in the R community, `sf` [@sf] and `tsibble`[@tsibble] have replaced `sp` and `xts` to be the convention structure for spatial and temporal data. One reason for their popularity is its integration with tidyverse ecosystem, making them intuitive and easy to adopt. For spatio-temporal data, we hope to build a data structure has the following features:

  1) A data structure that handles spatial and temporal dimension in a relational structure. This derives from the 3rd tidy data principal.
  2) An intuitive and easy to use interface that fits into the tidyverse ecosystem, and
  3) Compatibility with the latest spatial and temporal data structure. This would give users the flexibility to use work from existing packages.

\newpage
# Workflow/ Data pipeline

Now we introduce cubble in a data pipeline structure (review the concept of data pipeline? at least articulate its importance - automation, predictable of output)

## Spatio-temporal data in the wild

**Format of st in the wild**  
Analysing this type of data requires less considerations on the geographical geometry type and map projection but more on how measures in these fixed locations changes across the time domain and whether these changes are related for adjacent locations. For example, when nearby areas show patterns that are regular enough, visualising spatio-temporal data can 1) discover regional time series features, i.e. trend and seasonality, 2) find the Waldo sites from the crowd, and 3) see how correlation of nearby sites changes across time. \newline

**The main difficulty and challenge**  
The main difficulty in visualising this type of data is to show information in both space and time dimension with the proper level of details without information overflow. This would sometimes require aggregating the time dimension into the proper level or slicing the data into a reasonable number of subset for display. In this sense, a data structure that regulates the manipulation spatio-temporal data will benefit the analysis workflow. While many implementations focus on manipulating and visualising pure spatial or temporal data, there are not sufficient tools to deal with spatio-temporal data. The purpose of this paper is to introduce a spatio-temporal vector data structure for data analysis in R.

## Cubble

**We form a cubble by defining abc... - Nested and long form**  
When manipulating the spatial dimension it uses a nest form that:

### stretch

*By default build a nested cubble, stretch to long, create spatial attributes*

### tamp

*Tamp to nested, use the spatial attributes*

### Support on hierarchical structure

## Tidyverse compatibility

*list supported tidyverse functions*

## Others

## Australia precipitation pattern in 2020

Forming a cubble + basic tidyverse verbs - Vig 2
Aggregation  - Vig 4

## Matching precipitation and river level in Victria water gauges

Matching  - Vig 3

# Conclusion

# Old stuff

@@

@@

Below are the how the nested and long form look like for Australia climate data, which records daily precipitation, maximum and minimum temperature for 55 stations across Australia from 2015- 2020. Notice that each station forms a group in both forms and specifically, the nested  and long form have a underlying `rowwise_df` and `grouped_df` respectively.

With a cubic framework on mind, different types of manipulation with cubble can be thought of as slicing the cube in various way. The table below shows how some `dplyr` verbs are mapped into the operation in a cubble. With the existing grouping on the station, additional groupping can be added with `group_by` and removed with `ungrouped`. [talk about why it is useful]

@@

### 2021-11-22 main.tex
restructure the paper

Spatio-temporal data record changes of variables in spatially separated
regions across time. In this article, we consider spatio-temporal vector
data, which are recorded in a fixed interval and are point based,
characterised by longitude and latitude, in the spatial aspect. Examples
of this type of data include the house price of a city or county,
climate measures from weather stations in a country, and river level
data from electronic gauges.

Analysing this type of data requires less considerations on the
geographical geometry type and map projection but more on how measures
in these fixed locations changes across the time domain and whether
these changes are related for adjacent locations. For example, when
nearby areas show patterns that are regular enough, visualising
spatio-temporal data can 1) discover regional time series features,
i.e.~trend and seasonality, 2) find the Waldo sites from the crowd, and
3) see how correlation of nearby sites changes across time.

The main difficulty in visualising this type of data is to show
information in both space and time dimension with the proper level of
details without information overflow. This would sometimes require
aggregating the time dimension into the proper level or slicing the data
into a reasonable number of subset for display. In this sense, a data
structure that regulates the manipulation spatio-temporal data will
benefit the analysis workflow. While many implementations focus on
manipulating and visualising pure spatial or temporal data, there are
not sufficient tools to deal with spatio-temporal data. The purpose of
this paper is to introduce a spatio-temporal vector data structure for
data analysis in R.

The rest of the paper will be divided as follows: Section 2 reviews the
existing data structure for spatio, temporal, and spatio-temporal data.
Section 3 presents a new data structure for spatio-temporal data:
cubble. Then the paper introduces the workflow of data manipulation and
visualisation with the cubble structure in Section 4. Section 5 gives
some examples on how common spatial and temporal manipulations are
performed with cubble and how static and interactive visualisation help
to understand climate and {[}\ldots{]} data.

@@

Below we review some structure for spatial, temporal, and
spatio-temporal data.

@@

@@

@@

\hypertarget{manipulation}{%
\subsection{Manipulation}\label{manipulation}}

\hypertarget{mutate-and-filter}{%
\subsubsection{Mutate and filter}\label{mutate-and-filter}}

In the first example, we want to only keep the stations that have
\texttt{tmax} recorded in 2020. This requires first narrow down the
records to those in 2020, determine if \texttt{tmax} is missing for each
station, and then retain those stations that have \texttt{tmax}
recorded. The year filtering is an operation on the time axis, so we
start with the long form. Whether each station has \texttt{tmax}
recorded is a result of each station, rather than of each time point,
hence we need to switch to the nested form with \texttt{tamp()}. To
calculate whether \texttt{tmax} is recorded, we mutate a column
\texttt{tmax\_missing} that takes \texttt{TRUE} if all the \texttt{tmax}
in the nested list column \texttt{ts} are \texttt{NA} and \texttt{FALSE}
otherwise. To get the stations that we want, we need another filter on
\texttt{tmax\_missing}.

\begin{CodeChunk}
\begin{CodeInput}
R> aus_climate %>% 
+   stretch() %>% 
+   filter(year(date) == 2020) %>% 
+   tamp()
\end{CodeInput}
\begin{CodeOutput}
# cubble:   id [85]: nested form
# bbox:     [115.97, -43.32, 153.13, -12.42]- check gap on long
# temporal: date [date], prcp [dbl], tmax [dbl], tmin [dbl]
   id            lat  long  elev name                   wmo_id ts               
   <chr>       <dbl> <dbl> <dbl> <chr>                   <dbl> <list>           
 1 ASN00009021 -31.9  116.  15.4 perth airport           94610 <tibble [366 x 4~
 2 ASN00010311 -31.9  117. 179   york                    94623 <tibble [366 x 4~
 3 ASN00010614 -32.9  117. 338   narrogin                94627 <tibble [366 x 4~
 4 ASN00014015 -12.4  131.  30.4 darwin airport          94120 <tibble [366 x 4~
 5 ASN00015131 -17.6  134. 220   elliott                 94236 <tibble [366 x 4~
 6 ASN00016065 -30.4  137.  76   andamooka               95660 <tibble [366 x 4~
 7 ASN00023034 -35.0  139.   2   adelaide airport        94672 <tibble [366 x 4~
 8 ASN00023373 -34.5  139. 275   nuriootpa viticultural  94681 <tibble [366 x 4~
 9 ASN00024024 -34.4  141.  30.1 loxton research centre  94682 <tibble [366 x 4~
10 ASN00024048 -34.2  141.  31.5 renmark aero            95687 <tibble [366 x 4~
# ... with 75 more rows
\end{CodeOutput}
\end{CodeChunk}

\hypertarget{join}{%
\subsubsection{Join}\label{join}}

Now we want to select the stations that have been registered with world
meteorological organisation (WMO) and the dataset \texttt{station} has a
column \texttt{wmo\_id} that records this information. To do this task,
we first need to join the \texttt{station} dataset with our climate
dataset and then filter out those stations that don't have the WMO id.
Since the join is by station rather than by time, we start with the
nested form and write the exact same syntax of join and filter as with
tidyverse.

\begin{CodeChunk}
\begin{CodeInput}
R> # join wmo_id for each station
R> # to_join <- station %>% select(id, wmo_id)
R> # out <- climate_small %>% 
R> #   left_join(to_join, by = c("station" = "id")) %>% 
R> #   filter(!is.na(wmo_id))
R> # out
\end{CodeInput}
\end{CodeChunk}

Sometimes, we would like to have station-wise and time-wise variables in
the same form (i.e.~when plotting glyph maps). This can also be seen as
a joining task, on the long form, with the dataset to join being the
metadata. \texttt{migrate()} is a verb introduced as the shortcut for
\texttt{left\_join()} with a cubble's metadata and below is the
comparison of the two syntaxes.

\begin{CodeChunk}
\begin{CodeInput}
R> aus_climate %>% 
+   stretch() %>% 
+   migrate(id, lat, long)
\end{CodeInput}
\begin{CodeOutput}
# cubble:  date, id [85]: long form
# bbox:    [115.97, -43.32, 153.13, -12.42]- check gap on long
# spatial: lat [dbl], long [dbl], elev [dbl], name [chr], wmo_id [dbl]
   id          date        prcp  tmax  tmin   lat  long
   <chr>       <date>     <dbl> <dbl> <dbl> <dbl> <dbl>
 1 ASN00009021 2020-01-01     0  31.9  15.3 -31.9  116.
 2 ASN00009021 2020-01-02     0  24.9  16.4 -31.9  116.
 3 ASN00009021 2020-01-03     6  23.2  13   -31.9  116.
 4 ASN00009021 2020-01-04     0  28.4  12.4 -31.9  116.
 5 ASN00009021 2020-01-05     0  35.3  11.6 -31.9  116.
 6 ASN00009021 2020-01-06     0  34.8  13.1 -31.9  116.
 7 ASN00009021 2020-01-07     0  32.8  15.1 -31.9  116.
 8 ASN00009021 2020-01-08     0  30.4  17.4 -31.9  116.
 9 ASN00009021 2020-01-09     0  28.7  17.3 -31.9  116.
10 ASN00009021 2020-01-10     0  32.6  15.8 -31.9  116.
# ... with 31,100 more rows
\end{CodeOutput}
\end{CodeChunk}

\begin{itemize}
\tightlist
\item
  data quality check: filter out stations have variables not properly
  recorded
\item
  data summary:

  \begin{itemize}
  \tightlist
  \item
    daily -\textgreater{} monthly/ weekly,
  \item
    summarise by mean for tmax/ tmin, sum for prcp
  \end{itemize}
\item
\end{itemize}

\hypertarget{graphics}{%
\subsection{Graphics}\label{graphics}}

Static + interactive -\textgreater{} tooltip to show additional
information upon hovering

\begin{itemize}
\tightlist
\item
  Where are those stations on the map?

  \begin{itemize}
  \tightlist
  \item
    Mention mostly aero, airport, and lighthouse
  \end{itemize}
\end{itemize}

\renewcommand\refname{Summary}
\bibliography{references.bib}

>>>>

\textbf{Spatio-temporal data + examples}\\
Spatio-temporal data record changes of variables in spatially separated
regions across time. In this article, we consider spatio-temporal vector
data, which are recorded in a fixed interval. Examples of this type of
data include the house price of a city or county, climate measures from
weather stations in a country, and river level data from electronic
gauges \textcolor{red}{more examples here}. \newline

\textbf{point to common feature: spatial level variables + time level
variables relates to Table 13 in Tidy data paper}\\
Usually, this type of spatio-temporal data don't come in as a single
table. Tidy data principle (\ldots) prescribes each type of
observational unit to form a table. This would suggest two tables to
store the data, one for spatial-level and one for temporal-level. The
Table 13 in the tidy data paper present a structure like this and the
author argues the lack of tools to work with relational data. \newline

\textbf{My proposal}\\
Recent software development in R has proposed several relational data
structure: \texttt{tidygraph}\citep{tidygraph} for graph manipulation,
\texttt{dm} \citep{dm} for relational data model, while spatio-temporal
data could benefit from having its own relational data structure. In
this paper, we propose a tidy data structure for vector spaio-temporal
data. \newline

\textbf{Section division}\\
The rest of the paper will be divided as follows: Section 2 reviews the
existing data structure for spatio, temporal, and spatio-temporal data.
Section 3 presents a new data structure for spatio-temporal data:
cubble. Then the paper introduces the workflow of data manipulation and
visualisation with the cubble structure in Section 4. Section 5 gives
some examples on how common spatial and temporal manipulations are
performed with cubble and how static and interactive visualisation help
to understand climate and {[}\ldots{]} data. \newline

@@

\textbf{Existing packages}\\
Many data structures have been proposed for spatial and temporal data,
but not many for spatio-temporal data. One of the reason could be the
inherent different levels of information make it inefficient to store in
the same table. \texttt{spacetime}\citep{spacetime} proposed four
space-time layouts: Full grid (STF), sparse grid(STS), irregular (STI),
and trajectory (STT) based on underlying spatial structure \texttt{sp}
\citep{sp} and temporal structure \texttt{xts}\citep{xts}.
\texttt{spatstat} \citep{spatstat} implements a \texttt{ppp} class for
point pattern data. More recent package \texttt{stars} \citep{stars}
uses a spatiotemporal array to store the data and the array structure
has its influence from \texttt{cubelyr} \citep{cubelyr}, a dplyr data
cube backend. \newline

\textbf{Criteria of a data structure we want}

With recent development in the R community, \texttt{sf} \citep{sf} and
\texttt{tsibble}\citep{tsibble} have replaced \texttt{sp} and
\texttt{xts} to be the convention structure for spatial and temporal
data. One reason for their popularity is its integration with tidyverse
ecosystem, making them intuitive and easy to adopt. For spatio-temporal
data, we hope to build a data structure has the following features:

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  A data structure that handles spatial and temporal dimension in a
  relational structure. This derives from the 3rd tidy data principal.
\item
  An intuitive and easy to use interface that fits into the tidyverse
  ecosystem, and
\item
  Compatibility with the latest spatial and temporal data structure.
  This would give users the flexibility to use work from existing
  packages.
\end{enumerate}

\hypertarget{workflow-data-pipeline}{%
\section{Workflow/ Data pipeline}\label{workflow-data-pipeline}}

Now we introduce cubble in a data pipeline structure (review the concept
of data pipeline? at least articulate its importance - automation,
predictable of output)

\hypertarget{spatio-temporal-data-in-the-wild}{%
\subsection{Spatio-temporal data in the
wild}\label{spatio-temporal-data-in-the-wild}}

\textbf{Format of st in the wild}\\
Analysing this type of data requires less considerations on the
geographical geometry type and map projection but more on how measures
in these fixed locations changes across the time domain and whether
these changes are related for adjacent locations. For example, when
nearby areas show patterns that are regular enough, visualising
spatio-temporal data can 1) discover regional time series features,
i.e.~trend and seasonality, 2) find the Waldo sites from the crowd, and
3) see how correlation of nearby sites changes across time. \newline

\textbf{The main difficulty and challenge}\\
The main difficulty in visualising this type of data is to show
information in both space and time dimension with the proper level of
details without information overflow. This would sometimes require
aggregating the time dimension into the proper level or slicing the data
into a reasonable number of subset for display. In this sense, a data
structure that regulates the manipulation spatio-temporal data will
benefit the analysis workflow. While many implementations focus on
manipulating and visualising pure spatial or temporal data, there are
not sufficient tools to deal with spatio-temporal data. The purpose of
this paper is to introduce a spatio-temporal vector data structure for
data analysis in R.

\hypertarget{cubble}{%
\subsection{Cubble}\label{cubble}}

\textbf{We form a cubble by defining abc\ldots{} - Nested and long
form}\\
When manipulating the spatial dimension it uses a nest form that:

\hypertarget{stretch}{%
\subsubsection{stretch}\label{stretch}}

\emph{By default build a nested cubble, stretch to long, create spatial
attributes}

\hypertarget{tamp}{%
\subsubsection{tamp}\label{tamp}}

\emph{Tamp to nested, use the spatial attributes}

\hypertarget{support-on-hierarchical-structure}{%
\subsubsection{Support on hierarchical
structure}\label{support-on-hierarchical-structure}}

\hypertarget{tidyverse-compatibility}{%
\subsection{Tidyverse compatibility}\label{tidyverse-compatibility}}

\emph{list supported tidyverse functions}

\hypertarget{others}{%
\subsection{Others}\label{others}}

\hypertarget{australia-precipitation-pattern-in-2020}{%
\subsection{Australia precipitation pattern in
2020}\label{australia-precipitation-pattern-in-2020}}

Forming a cubble + basic tidyverse verbs - Vig 2 Aggregation - Vig 4

\hypertarget{matching-precipitation-and-river-level-in-victria-water-gauges}{%
\subsection{Matching precipitation and river level in Victria water
gauges}\label{matching-precipitation-and-river-level-in-victria-water-gauges}}

Matching - Vig 3

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

\hypertarget{old-stuff}{%
\section{Old stuff}\label{old-stuff}}

@@

Below are the how the nested and long form look like for Australia
climate data, which records daily precipitation, maximum and minimum
temperature for 55 stations across Australia from 2015- 2020. Notice
that each station forms a group in both forms and specifically, the
nested and long form have a underlying \texttt{rowwise\_df} and
\texttt{grouped\_df} respectively.

With a cubic framework on mind, different types of manipulation with
cubble can be thought of as slicing the cube in various way. The table
below shows how some \texttt{dplyr} verbs are mapped into the operation
in a cubble. With the existing grouping on the station, additional
groupping can be added with \texttt{group\_by} and removed with
\texttt{ungrouped}. {[}talk about why it is useful{]}

@@

\hypertarget{examples-1}{%
\section{Examples}\label{examples-1}}

@@

\bibliography{references.bib}
